Digital Analysis of Paintings

### 2014-04-26 paper.tex
Add paper 3.
Up to around 1.25k words :-) possibly writing a bit too much for each paper,
but we'll see.

\subsection{Pigment Mapping}
% Paper 3

>>>>

\subsection{Pigment Mapping}
% Paper 3
Colour analysis can also give a glimpse into the colour pigments the artist
used to create the work. Using a database of known oil pigments and
\textit{a priori} knowledge, it is possible to work out which pigments are used
in a painting, and also to be able to show which parts of the painting are made
up from which pigment\cite{zhao2008investigation}.

This is done through a process known a multispectral imaging, the process of
capturing a different frequencies to provide a different spectrum of light and
enable more analysis.

This technique is especially powerful for segmenting different pigments in an
image as each pigment is made up of a different substance.

Because this process requires both hardware and software it make a large
different whether the materials a work is made up of are known. When known it
can be possible to find the combinations of these materials at a given point
and their concentrations.

When the materials are unknown, extra processing is required to decide which
materials the painting comprises of. This process uses spectral processing but
also requires prior knowledge of the artist and art tools.

In the experimental results this paper provides, the latter is achieved by a
study of another of Van Gogh's works from the same time.

Pigment mapping across every pixel is a costly operation in terms of memory and
CPU time. This research makes a reasonable assumption that a similar colour
will have been painted using similar pigments to reduce the amount of pigment
mapping which occurs. This does lead to unwanted side-effects, but the only way
to combat these is to increase the number of pixels which pixel-mapping.

To reduce the number of pixels considered for pigment mapping the image is
first partitioned into a number of smaller images to reduce processing time on
the next steps

Each of these partitioned regions is then split into a number of clusters based
on the colours of the pixels. This was done using supervised and unsupervised
algorithms. The unsupervised algorithm was very sensitive and had long running
times whilst the supervised algorithm requires a human observer.

Finally pixels within these clusters were then selected based on the similarity
of pixels within the cluster, the clusters and partitioned images can then be
stitched back together and rendered based on the pigment maps.

This research could be incredibly useful if it could be applied to the analysis
of artwork and the field of multispectral analysis has already had a lot of
success in other fields.

However, because this is both a hardware- and software-based system, it may not
be something which can be used with regularity as it requires the physical
presence of the paintings, which not all artwork analysis researchers have
access to.

It also requires a lot of a priori knowledge of the artist and calculating the
materials a painting consists of may be a difficult, if not impossible task,
depending on the artist.

In conclusion, this technique can provide a very powerful analysis of a
painting, but at the cost of requiring specialised hardware, the physical
painting and expert knowledge about the artist, so is a very manual process.

This technique could be improved by using a less naive clustering unsupervised
algorithm to remove some of the need for human intervention, but the need for
the physical painting will always be a limiting factor of this work.
